Industrial Best Practice

### 2015-03-23 ibp/ibp.tex
Changes in section 3

@@

>>>>

Once this information has been fully analysed and documented, with the best practices found, the framework can be created in full. The framework needs to be language agnostic and apply to no specific technical area, rather it should be applicable to all.

@@

To ease the adoption process, a series of tests and evaluations will be performed on pilot studies. The goal of these pilot studies would be to verify and improve the best practices. For example, we will perform an analysis of an exist API and it's changes against an existing framework. We will then apply our framework and best practices to see if our framework suggests better and more robust changes, taking into account the affects of these changes on the ecosystem. Feedback will then be collected from the company who owns the API based on our frameworks suggested changes. This will be done to determine if our suggested changes are achieving the same goals as their changes would have done.
